Forecasting the 2024 US Presidential Election: A Poll-Based Approach

### 2024-10-22 paper/paper.qmd
Updated initial lm model and llm_usage

```{r}
data <- read.csv("../data/02-analysis_data/cleaned_president_polls.csv")
skim(data)

```

```{r}
colnames(data)
```

```{r pairplot}
#| warning: false
#| message: false

numeric_data <- data %>% 
  select(where(is.numeric)) %>% 
  select(numeric_grade, pollscore, transparency_score, sample_size, pct) %>% 
  filter(complete.cases(.))

# Create a pair plot
ggpairs(numeric_data)
```

```{r}
model <- data %>%
  filter(numeric_grade >= 2.0, candidate_name == "Kamala Harris") %>%
  lm(pct ~ numeric_grade + days_towards_election, data = .)

# Get the summary of the model
summary(model)
```

"pollster"                 
"sponsors"                               
"numeric_grade"             
"pollscore"                 
"methodology"               
"transparency_score"       
"state"                     
"start_date"                
"end_date"                 
"sponsor_candidate"         
"sponsor_candidate_party"        
"question_id"               
"sample_size"               
"population", "population_full",
"tracking", "notes"                     
"source"                    
"internal"                  
"partisan"                 
"race_id"                                 
"ranked_choice_reallocated" 
"ranked_choice_round"       
"hypothetical"              
"party"                    
"answer"                   
"candidate_name"            
"pct"

@@

>>>>

```{r}
#| echo: false
#| message: false
#| warning: false
#| include: false
data <- read.csv("../data/02-analysis_data/cleaned_president_polls.csv")
skim(data)
```

```{r pairplot}
#| warning: false
#| message: false
#| echo: false
numeric_data <- data %>% 
  select(where(is.numeric)) %>% 
  select(numeric_grade, pollscore, transparency_score) %>% 
  filter(complete.cases(.))

# Create a pair plot
ggpairs(numeric_data) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8, margin = margin(t = 10)),
    axis.text.y = element_text(size = 8, margin = margin(r = 10)),
    strip.text = element_text(size = 6)  # Adjusts the size of variable name tags
  )
```

@@

```{r}
#| echo: false
#| message: false
#| warning: false
candidate_names <- c("Kamala Harris", "Donald Trump")

# Define a function to fit the model and return the summary for each candidate
fit_model <- function(candidate) {
  candidate_data <- data %>%
    filter(candidate_name == candidate)

  model <- lm(pct ~ pollscore + transparency_score + days_towards_election, data = candidate_data)

  summary(model)
}

# Apply the function to each distinct candidate name and store the summaries in a list
model_summaries <- candidate_names %>%
  set_names() %>%
  map(fit_model)

# Print model summaries for each candidate
model_summaries
```
